\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-25 draft.tex
Language change in 4.3

In our initial experiments, we realised that Formula~\ref{eq:commu} is a
condition that is too strong for the reducer to be commutative. To illustrate
the issue, we present a simple example. In the loop body, the input is first
stored in a variable $t$ and this is then assigned to $s$, i.e., $t:=\cur;s:=t$.
After the loop, output the value of $s$. In this case, the $F$ function
returns the updated values of both $s$ and $t$ after the execution of the loop
body. Observe that $F(c_1, F(c_2,s,t)) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t))
= (c_1+c_2, c_2)$. It follows that Formula~\ref{eq:commu} is invalid. The second
component of the returned tuples, which causes the invalidity, corresponds to
the value of $t$ after executing the loop body twice. Their values are $c_1$ and
$c_2$, respectively, in $F(c_1, F(c_2,s,t))$ and $F(c_2, F(c_1,s,t))$. However,
in this case, the value of $t$ will not affect the output of the reducer.

>>>>

In our initial experiments, we realised that Formula~\ref{eq:commu} is a
condition that is too strong for the reducer to be commutative. To illustrate
the issue, we present a simple example. In the loop body, the input is first
stored in a variable $t$ and this is then assigned to $s$, i.e., $t:=\cur;s:=s+t$.
After the loop, the value of $s$ is output. In this case, the $F$ function
returns the updated values of both $s$ and $t$ after the execution of the loop
body. Observe that $F(c_1, F(c_2,s,t)) = (s+c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t))
= (s+c_1+c_2, c_2)$. It follows that Formula~\ref{eq:commu} is invalid. The second
component of the returned tuples, which causes the invalidity, corresponds to
the value of $t$ after executing the loop body twice. Their values are $c_1$ and
$c_2$, respectively, in $F(c_1, F(c_2,s,t))$ and $F(c_2, F(c_1,s,t))$. However,
in this case, the value of $t$ will not affect the output of the reducer.
